---
title: "Practial machine learning week4 assignment"
output: html_document
---

# The goal of this project
is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you built your model, how you used cross validation, what you think the expected out of sample error is, and why you made the choices you did. You will also use your prediction model to predict 20 different test cases.

# load packages
```{r}
library(doParallel)
library(caret)
library(randomForest)
```

# load data
Data files were downloaded from the designated url.
```{r}
train_url <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
training_data <- read.csv(url(train_url))
```

# data cleaning
Columns, which had index and many NA values (mean > 0.90), were removed. Moreover, colums with near zero-variation were removed. 
```{r}
# data cleaning; remove index column
training_data_01 <- training_data[,-c(1)]
# data cleaning; remove NAs
NA_col <- sapply(training_data_01, function(x) mean(is.na(x))) > 0.90
training_data_02 <- training_data_01[,NA_col == FALSE]
# data cleanining; non zero var
near_zero_var <- nearZeroVar(training_data_02)
training_data_03 <- training_data_02[,-near_zero_var]
```

# data partition
60% of cleaned training data was used for building a model, and the remaining data was used for testing the model to evaluate its accuracy.
```{r}
set.seed(191207)
inTrain <- createDataPartition(training_data_03$classe, p = 0.6, list = FALSE)
training <- training_data_03[inTrain,]
testing <- training_data_03[-inTrain,]
```

# Random Forest model
Random Forest model was selected for the prediction model. And, cross-validation was used as a resampling method.
```{r}
# parallel processing; n = 4
cl <- makePSOCKcluster(4)
registerDoParallel(cl)
# resampling method: cross validation
fitControl <- trainControl(method = "cv")
# building model
set.seed(0)
RF_mod <- train(classe ~.,
                   data = training,
                   method = "rf",
                   trControl=fitControl
                   )
# prediction and evaluation
RF_pred <- predict(RF_mod, testing)
RF_pred_conf <- confusionMatrix(RF_pred, testing$classe)
```

# summary
In the case of test data, the model showed accuracy value of >0.99 and its sample error rate is acceptable. Based on this test result, further exploration of predictive models was not conducted.
```{r}
RF_mod
RF_pred_conf
```